Software Citation Principles

### 2016-04-19 sc-principles/software-citation-principles.tex
added explanation of bullets to Table 2 caption

\caption{Use cases and basic metadata requirements for software citation, adapted from~\cite{SC-Use-Cases}.}

>>>>

\caption{
Use cases and basic metadata requirements for software citation, adapted from~\cite{SC-Use-Cases}.
Solid circles (\textbullet) indicate required metadata, while open circles (\textopenbullet) indicate recommended metadata.
}
